\ourlongtitle

### 2021-08-23 Bernoulli/AnswerReviews.tex

\documentclass[12pt]{amsart}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[round]{natbib}
\usepackage{amssymb,amsmath,latexsym,xcolor}

%\textwidth  14.5cm
%\textheight 20cm
%\voffset=-1cm
%\hoffset=-1cm

\newcommand{\rref}[1]{{\small \textcolor{gray}{#1}} }
\newcommand{\cl}[1]{ \textcolor{blue}{#1}}

\begin{document}

\begin{center}
\textbf{Answer to Referees for \textit{"A pseudo-marginal sequential Monte Carlo online smoothing algorithm"}}
\end{center}

\bigskip

We would like to thank the associate editor and the referees for the attention they paid to our work and their positive feedbacks.

\bigskip

Minor errors and typos listed by R2 were corrected as suggested. Pkease find below a few detailed answers.

\medskip

{\bf p.7 Just before 2.2.2, it would be nice to comment on where one might get suitable adjustment weights $\vartheta_n$ from. How are these to be chosen or tuned?}\\
{\em }

\medskip

{\bf p.29 Appendix A in the supplement has in the numerator that arises from . I think this should read instead?}\\
{\em The normalizing term given in the appendix is correct, see (2.10).}

\medskip

{\bf p.30 Appendix A has in the denominator for  which I think should read  as there is a dangling dxn+1 otherwise.}\\
{\em The denominator is correct the definition of $\mathsf{X}^n$ given in the appendix is $\mathsf{X}^n = \mathsf{X}_0 \times \ldots \times  \mathsf{X}_n$.}

\medskip

\end{document}

### 2021-08-23 Bernoulli/glo-2020-proof-asymp.tex
Corrected typos

\begin{proposition}
\label{prop:hoeffding:tau:marginal}
Assume \hypref[assum:biased:estimate]{assum:bound:filter:pseudomarginal}. Then for all $n \in \nset$, $h_n \in \bmaf{\Xfd^n}$, $(f_n, \ftd{n}) \in \bmf{\Xfd_n}^2$, and $\K \in \nsetpos$ there exist $(c_n, d_n) \in \rsetpos^2$ such that for all $\N \in \nsetpos$ and $\epsilon > 0$,
\begin{itemize}
\item[(i)] 
$ \displaystyle
\pP\left(\left| \frac{1}{\N} \sum_{i = 1}^\N \ewght{n}{i} \{\tstat[i]{n} f_n(\epart{n}{i}) + \ftd{n}(\epart{n}{i})\} - \frac{\postmod{n - 1} \ukmod{n - 1} ( \tstatmod{n} h_n f_n + \tilde{f}_n )}{\postmod{n - 1} \adjfuncforward{n - 1}} \right| \geq \epsilon \right) \leq c_n \exp \left( - d_n \N \epsilon^2 \right),
$
\item[(ii)] 
$ \displaystyle
\pP\left(\left| \sum_{i = 1}^\N \frac{\ewght{n}{i}}{\sumwght{n}} \{\tstat[i]{n} f_n(\epart{n}{i}) + \tilde{f}_n(\epart{n}{i})\} - \postmod{n} ( \tstatmod{n} h_n f_n + \tilde{f}_n ) \right| \geq \epsilon \right) \leq c_n \exp \left( - d_n \N \epsilon^2 \right).
$
\end{itemize}
\end{proposition}

@@

\begin{proof}[Proof of Proposition~\ref{prop:hoeffding:tau:marginal}]
We establish (i) by induction over $n$. Write, using Lemma~\ref{lem:expectation:incremental:marginal},
\begin{multline} \label{eq:hoeffding:decomp}
\frac{1}{\N} \sum_{i = 1}^\N \ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\} - \frac{\postmod{n} \ukmod{n} \{ \tstatmod{n + 1} h_{n + 1} f_{n + 1} + \ftd{n + 1} \}}{\postmod{n} \adjfuncforward{n}}  \\
= \frac{1}{\N} \sum_{i = 1}^\N \ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\} - \pE \left[ \ewght{n + 1}{1} \{\tstat[1]{n + 1} f_{n + 1}(\epart{n + 1}{1}) + \ftd{n + 1}(\epart{n + 1}{1})\} \cond \calF{n}{\N} \right] \\
+ \sum_{j = 1}^\N 
\frac{\ewght{n}{j} \adjfuncforward{n}(\epart{n}{j})}{\sum_{j' = 1}^\N \ewght{n}{j'} \adjfuncforward{n}(\epart{n}{j'})} \{ \tstat[j]{n} \prop{n} (\wgtfuncmod{n} f_{n + 1})(\epart{n}{j}) + \prop{n}(\wgtfuncmod{n} \addf{n} f_{n + 1} + \wgtfuncmod{n} \ftd{n + 1})(\epart{n}{j})\} \\
- \frac{\postmod{n - 1} \ukmod{n - 1}\{\tstatmod{n} \ukmod{n} f_{n + 1} + \ukmod{n} (\addf{n} f_{n + 1} + \ftd{n + 1})\}}{\postmod{n - 1} \ukmod{n - 1} \adjfuncforward{n}}. 
\end{multline}
Since for all $i$, 
$$
|\ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\}| \leq \| \wgtfunc{n} \|_\infty (\| h_{n + 1} \|_\infty \| f_{n + 1} \|_\infty + \| \ftd{n + 1} \|_\infty), 
$$
the Hoeffding inequality for conditional expectations provides constants $(d, \tilde{d}) \in \rsetpos^2$ such that for all $\epsilon > 0$, 
\begin{multline*}
\pP \left( \left| \frac{1}{\N} \sum_{i = 1}^\N \ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\} \right. \right. \\
\left. \left.  - \pE \left[ \ewght{n + 1}{1} \{\tstat[1]{n + 1} f_{n + 1}(\epart{n + 1}{1}) + \ftd{n + 1}(\epart{n + 1}{1})\} \cond \calF{n}{\N} \right] \vphantom{\sum_{i = 1}^\N} \right| \geq \epsilon \right) \leq d \exp \left( - \tilde{d} N \epsilon^2 \right).  
\end{multline*}
In addition, since $\adjfuncforward{n}$, $\adjfuncforward{n} \prop{n} (\wgtfuncmod{n} f_{n + 1})$, and $\adjfuncforward{n} \prop{n}(\wgtfuncmod{n} \addf{n} f_{n + 1} + \wgtfuncmod{n} \ftd{n + 1})$ all belong to $\bmf{\Xfd_n}$, there exist, by the induction hypothesis and \cite[Lemma~4]{douc:garivier:moulines:olsson:2010}, $(d', \tilde{d}') \in \rsetpos^2$ such that for all $\epsilon > 0$, 
\begin{multline*}
\pP \left( \left|  \sum_{j = 1}^\N 
\frac{\ewght{n}{j} \adjfuncforward{n}(\epart{n}{j})}{\sum_{j' = 1}^\N \ewght{n}{j'} \adjfuncforward{n}(\epart{n}{j'})} \{ \tstat[j]{n} \prop{n} (\wgtfuncmod{n} f_{n + 1})(\epart{n}{j}) + \prop{n}(\wgtfuncmod{n} \addf{n} f_{n + 1} + \wgtfuncmod{n} \ftd{n + 1})(\epart{n}{j})\} \right. \right. \\
\left. \left. - \frac{\postmod{n - 1} \ukmod{n - 1}\{\tstatmod{n} \ukmod{n} f_{n + 1} + \ukmod{n} (\addf{n} f_{n + 1} + \ftd{n + 1})\}}{\postmod{n - 1} \ukmod{n - 1} \adjfuncforward{n}} \right| \geq \epsilon \right) \leq d' \exp \left( - \tilde{d}' N \epsilon^2 \right).  
\end{multline*}
Combining the previous two inequalities completes the proof of (i) at time step $n + 1$. The base case $n = 1$ is established using again the decomposition \eqref{eq:hoeffding:decomp}, the standard Hoeffding inequality for independent and identically distributed variables, \cite[Lemma~4]{douc:garivier:moulines:olsson:2010}, and the fact that $h_0 \equiv 0$.

>>>>

\begin{proposition}
\label{prop:hoeffding:tau:marginal}
Assume \hypref[assum:biased:estimate]{assum:bound:filter:pseudomarginal}. Then for all $n \in \nset$, $h_n \in \bmaf{\Xfd^n}$, $(f_n, \ftd{n}) \in \bmf{\Xfd_n}^2$, and $\K \in \nsetpos$ there exist $(c_n, d_n) \in \rsetpos^2$ such that for all $\N \in \nsetpos$ and $\delta > 0$,
\begin{itemize}
\item[(i)] 
$ \displaystyle
\pP\left(\left| \frac{1}{\N} \sum_{i = 1}^\N \ewght{n}{i} \{\tstat[i]{n} f_n(\epart{n}{i}) + \ftd{n}(\epart{n}{i})\} - \frac{\postmod{n - 1} \ukmod{n - 1} ( \tstatmod{n} h_n f_n + \tilde{f}_n )}{\postmod{n - 1} \adjfuncforward{n - 1}} \right| \geq \delta \right) \leq c_n \exp \left( - d_n \N \delta^2 \right),
$
\item[(ii)] 
$ \displaystyle
\pP\left(\left| \sum_{i = 1}^\N \frac{\ewght{n}{i}}{\sumwght{n}} \{\tstat[i]{n} f_n(\epart{n}{i}) + \tilde{f}_n(\epart{n}{i})\} - \postmod{n} ( \tstatmod{n} h_n f_n + \tilde{f}_n ) \right| \geq \delta \right) \leq c_n \exp \left( - d_n \N \delta^2 \right).
$
\end{itemize}
\end{proposition}

@@

\begin{proof}[Proof of Proposition~\ref{prop:hoeffding:tau:marginal}]
We establish (i) by induction over $n$. Write, using Lemma~\ref{lem:expectation:incremental:marginal},
\begin{multline} \label{eq:hoeffding:decomp}
\frac{1}{\N} \sum_{i = 1}^\N \ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\} - \frac{\postmod{n} \ukmod{n} \{ \tstatmod{n + 1} h_{n + 1} f_{n + 1} + \ftd{n + 1} \}}{\postmod{n} \adjfuncforward{n}}  \\
= \frac{1}{\N} \sum_{i = 1}^\N \ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\} - \pE \left[ \ewght{n + 1}{1} \{\tstat[1]{n + 1} f_{n + 1}(\epart{n + 1}{1}) + \ftd{n + 1}(\epart{n + 1}{1})\} \cond \calF{n}{\N} \right] \\
+ \sum_{j = 1}^\N 
\frac{\ewght{n}{j} \adjfuncforward{n}(\epart{n}{j})}{\sum_{j' = 1}^\N \ewght{n}{j'} \adjfuncforward{n}(\epart{n}{j'})} \{ \tstat[j]{n} \prop{n} (\wgtfuncmod{n} f_{n + 1})(\epart{n}{j}) + \prop{n}(\wgtfuncmod{n} \addf{n} f_{n + 1} + \wgtfuncmod{n} \ftd{n + 1})(\epart{n}{j})\} \\
- \frac{\postmod{n - 1} \ukmod{n - 1}\{\tstatmod{n} \ukmod{n} f_{n + 1} + \ukmod{n} (\addf{n} f_{n + 1} + \ftd{n + 1})\}}{\postmod{n - 1} \ukmod{n - 1} \adjfuncforward{n}}. 
\end{multline}
Since for all $i$, 
$$
|\ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\}| \leq \| \wgtfunc{n} \|_\infty (\| h_{n + 1} \|_\infty \| f_{n + 1} \|_\infty + \| \ftd{n + 1} \|_\infty), 
$$
the Hoeffding inequality for conditional expectations provides constants $(d, \tilde{d}) \in \rsetpos^2$ such that for all $\delta > 0$, 
\begin{multline*}
\pP \left( \left| \frac{1}{\N} \sum_{i = 1}^\N \ewght{n + 1}{i} \{\tstat[i]{n + 1} f_{n + 1}(\epart{n + 1}{i}) + \ftd{n + 1}(\epart{n + 1}{i})\} \right. \right. \\
\left. \left.  - \pE \left[ \ewght{n + 1}{1} \{\tstat[1]{n + 1} f_{n + 1}(\epart{n + 1}{1}) + \ftd{n + 1}(\epart{n + 1}{1})\} \cond \calF{n}{\N} \right] \vphantom{\sum_{i = 1}^\N} \right| \geq \delta \right) \leq d \exp \left( - \tilde{d} N \delta^2 \right).  
\end{multline*}
In addition, since $\adjfuncforward{n}$, $\adjfuncforward{n} \prop{n} (\wgtfuncmod{n} f_{n + 1})$, and $\adjfuncforward{n} \prop{n}(\wgtfuncmod{n} \addf{n} f_{n + 1} + \wgtfuncmod{n} \ftd{n + 1})$ all belong to $\bmf{\Xfd_n}$, there exist, by the induction hypothesis and \cite[Lemma~4]{douc:garivier:moulines:olsson:2010}, $(d', \tilde{d}') \in \rsetpos^2$ such that for all $\delta > 0$, 
\begin{multline*}
\pP \left( \left|  \sum_{j = 1}^\N 
\frac{\ewght{n}{j} \adjfuncforward{n}(\epart{n}{j})}{\sum_{j' = 1}^\N \ewght{n}{j'} \adjfuncforward{n}(\epart{n}{j'})} \{ \tstat[j]{n} \prop{n} (\wgtfuncmod{n} f_{n + 1})(\epart{n}{j}) + \prop{n}(\wgtfuncmod{n} \addf{n} f_{n + 1} + \wgtfuncmod{n} \ftd{n + 1})(\epart{n}{j})\} \right. \right. \\
\left. \left. - \frac{\postmod{n - 1} \ukmod{n - 1}\{\tstatmod{n} \ukmod{n} f_{n + 1} + \ukmod{n} (\addf{n} f_{n + 1} + \ftd{n + 1})\}}{\postmod{n - 1} \ukmod{n - 1} \adjfuncforward{n}} \right| \geq \delta \right) \leq d' \exp \left( - \tilde{d}' N \delta^2 \right).  
\end{multline*}
Combining the previous two inequalities completes the proof of (i) at time step $n + 1$. The base case $n = 1$ is established using again the decomposition \eqref{eq:hoeffding:decomp}, the standard Hoeffding inequality for independent and identically distributed variables, \cite[Lemma~4]{douc:garivier:moulines:olsson:2010}, and the fact that $h_0 \equiv 0$.
